\documentclass[12pt, letterpaper]{article}
\usepackage{graphicx} % Required for inserting images

\title{Credit Card Fraud Detection}
\author{Huy Pham}
\date{October 2024}
\begin{document}

\maketitle

\section{Introduction}
    \subsection{Project Motivation}
        In 2021, the Federal Trade Commission (FTC) received nearly 390,000 reports of credit card fraud, making it one of the most common types of fraud in the U.S. This issue is projected to result in losses totaling \$165.1 billion over the next decade. Given the significant impact on society, leveraging machine learning technology to address this problem is increasingly beneficial.

    %Why is credit card fraud detection important? The impact of credit card fraud on financial institutions and consumers. 
    \subsection{Objective}
        In this project, our primary goal is to develop a reliable machine learning model for detecting fraudulent credit card transactions. This involves thorough analysis of the dataset to understand its distributions and engineering the most suitable model that captures the relationship between the target variable and features. We utilize Python's libraries like Scikit-learn, Matplotlib, Numpy, and Pandas for implementation and visualization. The dataset used for this project is sourced from Kaggle. However, its also important to note that this is an introductory project to machine learning.
    
        %What is the main goal of the project? (Building a model to detect fraudulent transactions.) Also mention the dataset and tools you plan on using.
 
\section{Dataset Overview}
    \subsection{Description}
        The dataset sourced from Kaggle, despite having 31 features, has only 3 known features (Time, Amount, and Class) due to security and privacy concerns.  
        %Provide details on the Credit Card Fraud Detection dataset from Kaggle.
        %Types of features that are in this data set
    \subsection{Classification}
        
    
        %How do you plan on using the data

\section{Methodology}

\section{Results}

\section{Conclusion}

%[**https://www.kaggle.com/datasets/mlg-ulb/creditcardfraud**](https://l.facebook.com/l.php?u=https%3A%2F%2Fwww.kaggle.com%2Fdatasets%2Fmlg-ulb%2Fcreditcardfraud%3Ffbclid%3DIwZXh0bgNhZW0CMTAAAR2tQWeDzS5OZRkOAH-tCtAoHJCSTXBJeMmNVBBxUs53ksxzQqrDg3Z_-Wg_aem_TxGTBgY4Fr21ezVddhdM-g&h=AT0bG5Pp0XKwHrLGFvLwLbClLKwKnuuVFhZqIozjoJ2_UC429ETRKIenNu1Hyl6cmdoT4h0iL1YEpOLSGa4UX0S3hJZ2utjJ7u6Sd3MX9Iivr5YsPiepLMMblnF-Fx8NfpZYbzP_kC8zET4Vv0SWpg)
\begin{thebibliography} {1}
    \bibitem{Bankrate}
    Egan, John. “Credit Card Fraud Statistics.” Bankrate, 12 Jan. 2023, www.bankrate.com/credit-cards/news/credit-card-fraud-statistics/?tpt=b.

    
\end{thebibliography}
    
\end{document}
